### 2020-05-25 paper/main.tex
added tex

\documentclass{article}
\usepackage{amsmath,amsthm,amssymb}
\usepackage{mathtext}
\usepackage[T2A]{fontenc}
\usepackage[utf8]{inputenc}
\usepackage[english]{babel}
\usepackage{graphicx}
\usepackage{hyperref}

\title{Capsule Based Aspect Extraction}
\author{Kirill Krasikov}
\date{May 2020}

\begin{document}
\maketitle
\begin{abstract}
    In the world of data science, more and more data is required to train models. Getting labeled datasets is a very expensive and lengthy process. In this regard, in the problems of thematic modeling, aspect extraction models from unplaced text is gaining popularity. These models allow, with minimal effort to annotate aspects, to structure the text into a set of topics or intentions. In this paper, a comparison is made of a SOTA model based on attention and a custom model in which the attention mechanism is replaced by a capsule network. Codes for paper: \url{https://github.com/KirillKrasikov/TopicModelingWithCapsNet}.
\end{abstract}

\section{Introduction}
First of all, you will need to write the whole report in English, with a few exceptions mentioned below.
This section is devoted to a problem motivation. You should answer the question of why the problem you were working on is important. Also, you should describe what is unique in your approach to this problem, what are the differences to other approaches.
\subsection{Team}
Please list your team members and describe their responsibilities. Example:

\textbf{Valentin Malykh} prepared this document.

\section{Related Work}
\label{sec:related}
In this section, you will describe in details the existing approaches to the problem you work on. For each approach, you need to provide a reference.

\cite{levenshtein1966binary} is a sample reference to the previous art. \cite{levenshtein1966dvoichnie} is a sample reference in Russian.

\section{Model Description}
Here you need to write a detailed description of your approach. It is important to mention that this description should give more details than the descriptions from section \ref{sec:related}\footnote{This is an example of internal references and footnotes at the same time.}.

You will likely be providing a figure to better present your approach. A sample circle is presented on Fig.~\ref{fig:circle}.

The other possible contents of this section are formulae. They could be on a new line:
$$S=\pi r^2,$$
or they could be inline, e.g. if you want to describe the used variables, like $S$ is an area of a circle, while $r$ is its radius.

\begin{figure}[!tbh]
    \centering
    \includegraphics[width=0.3\linewidth]{circle.png}
    \caption{A sample circle.}
    \label{fig:circle}
\end{figure}

\section{Dataset}
In this section, you need to describe the dataset(s) you are working with. 
An example dataset we will use is WikiText-2. Please mention a paper where it was presented, e.g. WikiText-2 was presented in \cite{merity2017pointer}. Please provide guidance on how to obtain the dataset\footnote{The one way to do it is to include a link to the website, where it could be downloaded from. Like \href{https://blog.einstein.ai/the-wikitext-long-term-dependency-language-modeling-dataset/}{this}.}. It is important to mention that the dataset you use must be available for the research purposes. So please make sure about that.

Your description will likely be including a table. On the Tab.~\ref{tab:statistics} you can see the statistics for the mentioned dataset. It is important to notice that there is a split of the dataset and this split is covered by the description.

\begin{table}[tbh!]
\begin{center}
\begin{tabular}[t]{|l|ccc|}
\hline
%\cline{2-4}
 & Train & Valid & Test \\
\hline
Articles & 600 & 60 & 60  \\
Tokens& 2,088,628 & 217,646 & 245,569 \\
Vocabulary size & \multicolumn{3}{c|}{33,278} \\
Out of Vocab rate &  \multicolumn{3}{c|}{2.6\%}  \\
\hline
\end{tabular}
\caption{Statistics of the WikiText-2. The out of vocabulary (OoV) rate notes what percentage of tokens have been replaced by an $\langle unk \rangle$ token. The token count includes newlines which add to the structure of the dataset.}
\label{tab:statistics}
\end{center}
\end{table}

If you were collecting the dataset on your own please describe the collection procedure, like criteria were used to filter the documents, the pre-processing steps, etc. It is nice if you release your dataset for the public. So please make sure that you have legal rights to collect and distribute the data you were working with. We recommend you to look at C4Corpus and how it is licensed to make your corpora. C4Corpus is described in \cite{habernal2016c4corpus}.

\section{Experiments}
This section should include several subsections.
\subsection{Metrics}
First of all, you should describe the metric(s) you were using to evaluate your approach. Most likely a metric description will include a formula.

\subsection{Experiment Setup}
Secondly, you need to describe the design of your experiment, e.g. how many runs there were, how the data split was done. The important details of your model, like hyper-parameters used in the experiments, and so on.

\subsection{Baselines}
Another important feature is that you could provide here the description of some simple approaches for your problem, like logistic regression over TF-IDF embedding for text classification. The baselines are needed is there is no previous art on the problem you are presenting.

\section{Results}
In this section, you need to list and describe the achieved results. It is crucial to have the results of the experiments for the other approaches. This is needed to be able to compare your results with some competitors. Most preferably, you should provide some references with results on the same problem.

Almost inevitably the results are presented as a table, but it is also possible to have a graph, i.e. a figure.

You need also to provide an interpretation of the presented results, to describe some features. E.g. your approach shows higher results on the short texts or by one metric instead of another.

Also in this section, you could provide some results for your model inference. The samples could be found in Tab.~\ref{tab:output}.

\begin{table}[!tbh]
    \centering
    \begin{tabular}{|c|}
\hline
Это пример вывода вашей модели на русском.\\
This is a sample output of your model in English.
\\
\hline
    \end{tabular}
    \caption{Output samples.}
    \label{tab:output}
\end{table}

\section{Conclusion}
In this section, you need to describe all the work in short: what you have done and what has been achieved. E.g. you have collected a dataset, made a markup for it and developed a model showing the best results compared to other models.

\bibliographystyle{apalike}
\bibliography{lit}
\end{document}

### 2020-05-25 paper/main.tex
updated paper

@@
 These models allow, with minimal effort to annotate aspects, to structure the text into a set of topics or intentions.
-In this paper, a comparison is made of a SOTA model based on attention and a custom model in which the attention mechanism is replaced by a capsule network.
+In this paper, a comparison is made of a SotA model based on attention and a custom model in which the attention mechanism is replaced by a capsule network with dynamic routings.
     Codes for paper: \url{https://github.com/KirillKrasikov/TopicModelingWithCapsNet}.
@@
 \section{Introduction}
+Aspect extraction is an important and challenging task in aspect-based sentiment analysis.
+For example, in the sentence "The beef was tender and melted in my mouth", the aspect term is "beef".
+Two sub-tasks are performed in aspects extraction: (1) extracting all aspects terms(e.g., "beef") from a review corpus, (2) clustering aspect terms with similar meaning into categories where each category represents a single aspect(e.g., cluster "beef", "pork", "pasta", and "tomato" into one aspect food) \cite{He2018ABAE}.
+
 First of all, you will need to write the whole report in English, with a few exceptions mentioned below.

### 2020-05-28 paper/main.tex
updated paper

@@
 Two sub-tasks are performed in aspects extraction: (1) extracting all aspects terms(e.g., "beef") from a review corpus, (2) clustering aspect terms with similar meaning into categories where each category represents a single aspect(e.g., cluster "beef", "pork", "pasta", and "tomato" into one aspect food) \cite{He2018ABAE}.
+in 2017 year, Unsupervised Aspect Extraction \cite{He2018ABAE} have become the dominant unsupervised approach for aspect extraction.
+In that work neural word embeddings map words with the same context to nearby points in the embedding space \cite{Mikolov2013W2V}.
+Then attention mechanism \cite{Bahdanau2015NMT} filter the word embeddings within a sentence and filtered words use to construct aspect embeddings.
+The training process for aspect embeddings is analogous to autoencoders, where dimension reduction use to extract the common factors among embedded sentences and reconstruct each sentence through a linear combination of aspect embeddings.
+The attention mechanism deemphasizes words that are not part of any aspects, allowing the model to focus on aspect words.
+That model call \textit{Attention-based Aspect Extraction} (ABAE).
 

### 2020-05-29 paper/main.tex
added paper introduction

@@
 That model call \textit{Attention-based Aspect Extraction} (ABAE).
-
-First of all, you will need to write the whole report in English, with a few exceptions mentioned below.
-This section is devoted to a problem motivation.
-You should answer the question of why the problem you were working on is important.
-Also, you should describe what is unique in your approach to this problem, what are the differences to other approaches.
-\subsection{Team}
-Please list your team members and describe their responsibilities. Example:
-
-\textbf{Valentin Malykh} prepared this document.
+In the same year "Google brain" suggested approach called \textit{Dynamic Routing Between Capsules} \cite{Hinton2017DRBC}.
+A capsule is a group of neurons whose activity vector represents the instantiation parameters of a specific type of entity such as an object or an object part.
+The length of the activity vector use to represent the probability that the entity exists and its orientation use to represent the instantiation parameters.
+Active capsules at one level make predictions, via transformation matrices, for the instantiation parameters of higher-level capsules.
+When multiple predictions agree, a higher level capsule becomes active.
+To best performance use iterative routing-by-agreement mechanism: A lower-level capsule prefers to send its output to higher level capsules whose activity vectors have a big scalar product with the prediction coming from the lower-level capsule \cite{Hinton2017DRBC}.
+In this work i implement ABAE model using pytorch, then change attention mechanism to capsule network and evaluate this models on Citysearch corpus used by previous works\cite{Ganu2009BeyondTheStars}\cite{Brody2010UAS}\cite{Zhao2010JMA}\cite{He2018ABAE}.
 

### 2020-05-29 paper/main.tex
added related work

@@
 \label{sec:related}
-In this section, you will describe in details the existing approaches to the problem you work on. For each approach, you need to provide a reference.
+The problem of aspect extraction has been well studied in the past decade.
+Initially, methods were mainly based on manually defined rules.
+\cite{HuLiu2004} proposed to extract different product features through finding frequent nouns and noun phrases.
+They also extracted opinion terms by finding the synonyms and antonyms of opinion seed words through WordNet.
+Following this, a number of methods have been proposed based on freequent item mining and dependency information to extract product aspects \cite{Zhuang2006} \cite{Somasundarn2009} \cite{Qiu2011}.
+These models heavily depend on predefined rules which work well only when the aspect terms are restricted to a small group of nouns.
+Supervised learning approaches generally model aspect extraction as a standard sequence labeling problem.
+\cite{Jin2009} \cite{Li2010} proposed to use hidden Markov models(HMM) and conditional random fields(CRF) respectively with a set of manually-extracted features.
+More recently, different neural models \cite{Yin2016} \cite{Wang2016} were proposed to automatically learn features for CRF-based aspect extraction.
+Rule-based models are usually not refined enough to categorize the extracted aspect terms.
+On the other hand, supervised learning requires large amounts of labeled data for training purposes.
+
+Unsupervised approaches, especially topic models, have been proposed subsequently to avoid reliance on labeled data.
+Generally, the outputs of those models are word distributions or rankings for each aspect.
+Aspects are naturally obtained without separately performing extraction and categorization.
+Most existing works \cite{Brody2010UAS} \cite{Zhao2010JMA} \cite{Mukherjee2012} \cite{Chen2014} are based on variants and extensions of LDA \cite{Blei2003}.
+Recently, \cite{Wang2015} relies on a substantial amount of prior knowledge such as part-of-speech(POS) tagging and sentiment lexicons.
+A biterm topic models (BTM) that generates co-occurring word pairs was proposed in \cite{Yan2013}.
+
+Attention models \cite{Mnih2014} have recently gained popularity in training neural networks and have been applied to various natural language processing tasks, including machine translation \cite{Bahdanau2015NMT}, sentence summarization \cite{Rush2015}, sentiment classification
 

### 2020-05-29 paper/main.tex
added model description

--- 2020-05-28 paper/main.tex
@@
-\documentclass{article}
-\usepackage{amsmath,amsthm,amssymb}
-\usepackage{mathtext}
-\usepackage[T2A]{fontenc}
-\usepackage[utf8]{inputenc}
-\usepackage[english]{babel}
-\usepackage{graphicx}
-\usepackage{hyperref}
+@article{He2018ABAE,
+title={An Unsupervised Neural Attention Model for Aspect Extraction},
+author={Ruidan He, Wee Sun Lee, Hwee Tou Ng, Daniel Dahlmeirer},
+year={2017},
+}
 
-\title{Capsule Based Aspect Extraction}
-\author{Kirill Krasikov}
-\date{May 2020}
+@article{Mikolov2013W2V,
+title={Efficient Estimation of Word Representations in Vector Space},
+author={Tomas Mikolov, Kai Chen, Greg Corrado, Jeffrey Dean},
+year={2017},
+}
 
-\begin{document}
-\maketitle
-\begin{abstract}
-    In the world of data science, more and more data is required to train models.
-Getting labeled datasets is a very expensive and lengthy process.
-In this regard, in the problems of thematic modeling, aspect extraction models from unplaced text is gaining popularity.
-These models allow, with minimal effort to annotate aspects, to structure the text into a set of topics or intentions.
-In this paper, a comparison is made of a SotA model based on attention and a custom model in which the attention mechanism is replaced by a capsule network with dynamic routings.
-    Codes for paper: \url{https://github.com/KirillKrasikov/TopicModelingWithCapsNet}.
-\end{abstract}
+@article{Bahdanau2015NMT,
+title={Neural Machine Translation by Jointly Learning to Align and Translate},
+author={Dzmitry Bahdanau, Kyunghyun Cho, Yoshua Bengio},
+year={2015},
+}
 
-\section{Introduction}
-Aspect extraction is an important and challenging task in aspect-based sentiment analysis.
-For example, in the sentence "The beef was tender and melted in my mouth", the aspect term is "beef".
-Two sub-tasks are performed in aspects extraction: (1) extracting all aspects terms(e.g., "beef") from a review corpus, (2) clustering aspect terms with similar meaning into categories where each category represents a single aspect(e.g., cluster "beef", "pork", "pasta", and "tomato" into one aspect food) \cite{He2018ABAE}.
-in 2017 year, Unsupervised Aspect Extraction \cite{He2018ABAE} have become the dominant unsupervised approach for aspect extraction.
-In that work neural word embeddings map words with the same context to nearby points in the embedding space \cite{Mikolov2013W2V}.
-Then attention mechanism \cite{Bahdanau2015NMT} filter the word embeddings within a sentence and filtered words use to construct aspect embeddings.
-The training process for aspect embeddings is analogous to autoencoders, where dimension reduction use to extract the common factors among embedded sentences and reconstruct each sentence through a linear combination of aspect embeddings.
-The attention mechanism deemphasizes words that are not part of any aspects, allowing the model to focus on aspect words.
-That model call \textit{Attention-based Aspect Extraction} (ABAE).
+@article{Hinton2017DRBC,
+title={Dynamic Routing Between Capsules},
+author={Sara Sabour, Nicholas Frosst, Geoffrey E Hinton},
+year={2017},
+}
 
-First of all, you will need to write the whole report in English, with a few exceptions mentioned below.
-This section is devoted to a problem motivation.
-You should answer the question of why the problem you were working on is important.
-Also, you should describe what is unique in your approach to this problem, what are the differences to other approaches.
-\subsection{Team}
-Please list your team members and describe their responsibilities. Example:
+@article{Ganu2009BeyondTheStars,
+title={Beyond the Stars: Improving Rating Predictions using Review Text Content},
+author={Gayatree Ganu, Noemie Elhadad, Amelie Marian},
+year={2009},
+booktitle={Proceedings of the 12th International Workshop on the Web and Databases},
+}
 
-\textbf{Valentin Malykh} prepared this document.
+@article{Zhao2010JMA,
+title={Jointly modeling aspects and opinions with a MaxEnt-LDA hybrid},
+author={Wayne Xin Zhao, Jing Jiang, Hongfei Yan, Xiaoming Li},
+year={2010},
+booktitle={Proceedings of the 2010 Conference on Emperical Methods in Natural Language Processing}
+}
 
-\section{Related Work}
-\label{sec:related}
-In this section, you will describe in details the existing approaches to the problem you work on. For each approach, you need to provide a reference.
+@article{HuLiu2004,
+title={Mining and summarizing customer reviews},
+author={Minqing Hu, Bing Liu},
+year={2004},
+booktitle={Proceedings of the 10th ACM SIGKDD International Conference on Knowledge Dicovery and Data Mining}
+}
 
-\cite{levenshtein1966binary} is a sample reference to the previous art. \cite{levenshtein1966dvoichnie} is a sample reference in Russian.
+@article{Zhuang2006,
+title={Movie review mining and summarization},
+author={Li Zhuang, Feng Jing, Xiao-Yan Zhu},
+year={2006},
+booktitle={Proceedings of the 15th ACM International Conference on Information and Knowledge Management}
+}
 
-\section{Model Description}
-Here you need to write a detailed description of your approach.
-It is important to mention that this description should give more details than the descriptions from section \ref{sec:related}\footnote{This is an example of internal references and footnotes at the same time.}.
+@article{Somasundarn2009,
+title={Recognizing stances in online debates},
+author={Swapna Somasundaran, Janyce Wiebe},
+year={2009},
+booktitle={Proceedings of the Joint Conference of the 47th Annual Meeting of the ACL and the 4th International Joint Conference on Natural Language Processing of the AFNLP}
+}
 
-You will likely be providing a figure to better present your approach. A sample circle is presented on Fig.~\ref{fig:circle}.
+@article{Qiu2011,
+title={Opinion word expansion and target extraction thorugh double propagation},
+author={Guang Qiu, Bing Liu, Jiajun Bu, Chun Chen},
+year={2011},
+journal={Computation Linguistics},
+volume={37},
+pages={9-27}
+}
 
-The other possible contents of this section are formulae. They could be on a new line:
-$$S=\pi r^2,$$
-or they could be inline, e.g. if you want to describe the used variables, like $S$ is an area of a circle, while $r$ is its radius.
+@article{Jin2009,
+title={A novel lexicallized HMM-based learning frameworks for web opinion mining},
+author={Wei Jin, Huang Hay Ho},
+year={2009},
+booktitle={Proceedings of the 26th International Conference on Machine Learning}
+}
 
-\begin{figure}[!tbh]
-    \centering
-    \includegraphics[width=0.3\linewidth]{circle.png}
-    \caption{A sample circle.}
-    \label{fig:circle}
-\end{figure}
+@article{Li2010,
+title={Structure-aware review mining and summarization},
+author={Fangtao Li, Chao Han, Minlie Huang, Xiaoyan Zhu, Ying-Ju Xia, Shu Zang, Hao Yu},
+year={2010},
+booktitle={Proceedings of the 23rd International Conference on Computer Linguistics}
+}
 
-\section{Dataset}
-In this section, you need to describe the dataset(s) you are working with. 
-An example dataset we will use is WikiText-2.
-Please mention a paper where it was presented, e.g.
-WikiText-2 was presented in \cite{merity2017pointer}.
-Please provide guidance on how to obtain the dataset\footnote{The one way to do it is to include a link to the website, where it could be downloaded from.
-Like \href{https://blog.einstein.ai/the-wikitext-long-term-dependency-language-modeling-dataset/}{this}.}.
-It is important to mention that the dataset you use must be available for the research purposes.
-So please make sure about that.
+@article{Li2010,
+title={Structure-aware review mining and summarization},
+author={Fangtao Li, Chao Han, Minlie Huang, Xiaoyan Zhu, Ying-Ju Xia, Shu Zang, Hao Yu},
+year={2010},
+booktitle={Proceedings of the 23rd International Conference on Computer Linguistics}
+}
 
-Your description will likely be including a table.
-On the Tab.~\ref{tab:statistics} you can see the statistics for the mentioned dataset.
-It is important to notice that there is a split of the dataset and this split is covered by the description.
+@article{Yin2016,
+title={Unsupervised word and dependency path embeddings for aspect term extraction},
+author={Yichun Yin, Furu Wei, Li Dong, Kaiming Xu, Ming Zhang Ming Zhou},
+year={2016},
+booktitle={Proceedings of the 25th International Joint Conference on Artificial Intelligence}
+}
 
-\begin{table}[tbh!]
-\begin{center}
-\begin{tabular}[t]{|l|ccc|}
-\hline
-%\cline{2-4}
- & Train & Valid & Test \\
-\hline
-Articles & 600 & 60 & 60  \\
-Tokens& 2,088,628 & 217,646 & 245,569 \\
-Vocabulary size & \multicolumn{3}{c|}{33,278} \\
-Out of Vocab rate &  \multicolumn{3}{c|}{2.6\%}  \\
-\hline
-\end{tabular}
-\caption{Statistics of the WikiText-2.
-The out of vocabulary (OoV) rate notes what percentage of tokens have been replaced by an $\langle unk \rangle$ token.
-The token count includes newlines which add to the structure of the dataset.}
-\label{tab:statistics}
-\end{center}
-\end{table}
+@article{Wang2016,
+title={Recursive neural conditional random fields for aspect-based sentiment analysis},
+author={Wenya Wang, Sinno J. Pan, Daniel Dahlmeier, Xiaokui Xiao},
+year={2016},
+booktitle={Proceedings of the 2016 Conference on Empirical Methods in Natural Language Processing}
+}
 
-If you were collecting the dataset on your own please describe the collection procedure, like criteria were used to filter the documents, the pre-processing steps, etc.
-It is nice if you release your dataset for the public.
-So please make sure that you have legal rights to collect and distribute the data you were working with.
-We recommend you to look at C4Corpus and how it is licensed to make your corpora.
-C4Corpus is described in \cite{habernal2016c4corpus}.
+@article{Brody2010UAS,
+title={An unsupervised aspect-sentiment model for online reviews},
+author={Samuel Brody, Noemie Elhadad},
+year={2010},
+booktitle={Human Language Technologies: The 2010 Annual Conference of the North American Chapter of the Association for Computational Linguistics}
+}
 
-\section{Experiments}
-This section should include several subsections.
-\subsection{Metrics}
-First of all, you should describe the metric(s) you were using to evaluate your approach. Most likely a metric description will include a formula.
+@article{Mukherjee2012,
+title={Aspect extraction through semi-supervised modelling},
+author={Arjun Mukkerjee, Bing Liu},
+year={2012},
+booktitle={Proceedings of the 50th Annual Meetings of the Association for Computational Linguistics}
+}
 
-\subsection{Experiment Setup}
-Secondly, you need to describe the design of your experiment, e.g.
-how many runs there were, how the data split was done.
-The important details of your model, like hyper-parameters used in the experiments, and so on.
+@article{Chen2014,
+title={Aspect extraction with automated prior knowledge learning},
+author={Zhiyuan Chen, Arjun Mukherjee, Bing Liu},
+year={2014},
+booktitle={Proceedings of the 52nd Annual Meeting of the Association for Computational Linguistics}
+}
 
-\subsection{Baselines}
-Another important feature is that you could provide here the description of some simple approaches for your problem, like logistic regression over TF-IDF embedding for text classification.
-The baselines are needed is there is no previous art on the problem you are presenting.
+@article{Blei2003,
+title={Latent Dirichlet allocation},
+author={David Blei, Andrew Ng, Michael Jordan},
+year={2003},
+journal={Jornal of Machine Learning research},
+volume={3},
+pages={993-1022}
+}
 
-\section{Results}
-In this section, you need to list and describe the achieved results.
-It is crucial to have the results of the experiments for the other approaches.
-This is needed to be able to compare your results with some competitors.
-Most preferably, you should provide some references with results on the same problem.
+@article{Wang2015,
+title={Sentiment-aspect extraction based on restricted Boltzmann machines},
+author={Linlin Wang, Kang Liu, Zhu Cao, Jun Zhao, Gerrard de Malo},
+year={2015},
+booktitle={Proceedings of the 53rd Annual Meeting of the Association for Computational Linguistics and the 7th International Joint Conference on Natural Language Processing}
+}
 
-Almost inevitably the results are presented as a table, but it is also possible to have a graph, i.e. a figure.
+@article{Yan2013,
+title={A biterm topic model for short texts},
+author={Xiaohui Yan, Jiafeng Guo, Yanyan Lan, Xueqi Cheng},
+year={2013},
+booktitle={Proceedings of the 22nd International World Wide Web Conference}
+}
 
-You need also to provide an interpretation of the presented results, to describe some features. E.g. your approach shows higher results on the short texts or by one metric instead of another.
+@article{Mnih2014,
+title={Recurrent models of visual attention},
+author={Volodymyr Mnih, Nicolas Heess, Alex Graves, Koray Kavukcuoglu},
+year={2014},
+booktitle={Advanced in Neural information Processing Systems}
+}
 
-Also in this section, you could provide some results for your model inference. The samples could be found in Tab.~\ref{tab:output}.
+@article{Rush2015,
+title={A neural attention model for sentence summarization},
+author={Alexander Rush, Sumit Chopa, Jason Weston},
+year={2015},
+booktitle={Proceeding of the 2015 Conference on Emperical Methods in Natural Language Processing}
+}
 
-\begin{table}[!tbh]
-    \centering
-    \begin{tabular}{|c|}
-\hline
-Это пример вывода вашей модели на русском.\\
-This is a sample output of your model in English.
-\\
-\hline
-    \end{tabular}
-    \caption{Output samples.}
-    \label{tab:output}
-\end{table}
+@article{Chen2016,
+title={Neural sentiment classification with user and product attention},
+author={Huimi Chen, Maosong Sun, Cunchao Tu, Yankai Lin, Zhiyuan Liu},
+year={2016},
+booktitle={Proceeding of the 2016 Conference on Emperical Methods in Natural Language Processing}
+}
 
-\section{Conclusion}
-In this section, you need to describe all the work in short: what you have done and what has been achieved.
-E.g.
-you have collected a dataset, made a markup for it and developed a model showing the best results compared to other models.
+@article{Herman2015,
+title={Teaching machines to read and comperhend},
+author={Karl Mortiz Hermann, Tomas Kocisky, Edward Grefenstette, Lasse Espeholt, Will Kay, Mustafa Suleyman, Phil Blunsom},
+year={2015},
+booktitle={Advanced in Neural Information Processing System}
+}
 
-\bibliographystyle{apalike}
-\bibliography{lit}
-\end{document}
+@article{Zhao2018,
+title={Investigationg Capsule Network with Dynamic ROuting for Text Classification},
+author={Wei Zhao, Jiambo Ye, Min Yang, Zeyang Lei, Suofei Zhang, Zhou Zhao},
+year={2018}
+}
+
+@article{levenshtein1966binary,
+title={Binary Codes Capable of Correcting Deletions, Insertions and Reversals},
+author={Levenshtein, Vladimir I.},
+year={1966},
+month={February},
+journal={Soviet Physics Doklady},
+volume={10},
+pages={709}
+}
+
+@article{levenshtein1966dvoichnie,
+title={Двоичные коды с исправлением выпадений, вставок и замещений символов},
+author={Левенштейн, {\CYRV}ладимир {\CYRI}осифович.},
+year={1966},
+month={February},
+journal={Доклады Академий Наук СССР},
+volume={163},
+pages={845--848},
+number={4}
+}
+
+@inproceedings{merity2017pointer,
+  title={Pointer sentinel mixture models},
+  author={Merity, Stephen and Xiong, Caiming and Bradbury, James and Socher, Richard},
+  booktitle={Proceedings of International Conference of Learning Representation},
+  year={2017}
+}
+
+@inproceedings{habernal2016c4corpus,
+  title={C4Corpus: Multilingual Web-size corpus with free license},
+  author={Habernal, Ivan and Zayed, Omnia and Gurevych, Iryna},
+  booktitle={Proceedings of the Tenth International Conference on Language Resources and Evaluation (LREC'16)},
+  pages={914--922},
+  year={2016}
+}

### 2020-05-29 paper/main.tex
added experiment template

--- 2020-05-29 paper/main.tex
@@
 To best performance use iterative routing-by-agreement mechanism: A lower-level capsule prefers to send its output to higher level capsules whose activity vectors have a big scalar product with the prediction coming from the lower-level capsule \cite{Hinton2017DRBC}.
-In this work i implement ABAE model using pytorch, then change attention mechanism to capsule network and evaluate this models on Citysearch corpus used by previous works\cite{Ganu2009BeyondTheStars}\cite{Brody2010UAS}\cite{Zhao2010JMA}\cite{He2018ABAE}.
+In this work i implement ABAE model using pytorch, then change attention mechanism to capsule network and evaluate this models on Citysearch corpus used by previous works \cite{Ganu2009BeyondTheStars} \cite{Brody2010UAS} \cite{Zhao2010JMA} \cite{He2018ABAE}.
 
@@
 
-Attention models \cite{Mnih2014} have recently gained popularity in training neural networks and have been applied to various natural language processing tasks, including machine translation \cite{Bahdanau2015NMT}, sentence summarization \cite{Rush2015}, sentiment classification
+Attention models \cite{Mnih2014} have recently gained popularity in training neural networks and have been applied to various natural language processing tasks, including machine translation \cite{Bahdanau2015NMT}, sentence summarization \cite{Rush2015}, sentiment classification \cite{Chen2016} and question answering \cite{Herman2015}.
+Rather than using all available inforamtion, attention mechanism aims to focus on the most pertinent information for a task.
+\cite{He2018ABAE} apply attention to an unsupervised neural model and demonstrate its effectiveness for aspect extraction.
 
-\cite{levenshtein1966binary} is a sample reference to the previous art. \cite{levenshtein1966dvoichnie} is a sample reference in Russian.
+\cite{Zhao2018} explore capsule networks with dynamic routing process \cite{Hinton2017DRBC} for supervised text classification.
+In this work i apply capsule network with dynamic routing to unsupervised neural model and evaluate experimental results with ABAE and others aspect extraction models.
 
 \section{Model Description}
-Here you need to write a detailed description of your approach.
-It is important to mention that this description should give more details than the descriptions from section \ref{sec:related}\footnote{This is an example of internal references and footnotes at the same time.}.
 
-You will likely be providing a figure to better present your approach. A sample circle is presented on Fig.~\ref{fig:circle}.
+The ultimate goal of Capsule Based Aspect Extraction (CBAE) is to learn a set of aspect embeddings, where each aspect can be interpreted by looking at the nearest words (representative words) in the embedding space.
+Each word $w$ in vocabulary with a feature vector $e_w \in \R^d$ \cite{He2018ABAE}.
+Word embeddings use to map words that often co-occur in a context to points that are close by in the embedding space \cite{Mikolov2013W2V}.
+The feature vectors associated with the words correspond to the rows of a word embedding matrix $E \in R^{Vd}$, where $V$ is the vocabulary size.
+Model try to learn embeddings of aspects, where aspects share the same embedding space with words.
+This requires an aspect embedding matrix $T \in R^{Vd}$, where $K$ - the number of aspects ($K$ much smaller than $V$).
+The aspect embeddings are use to approximate the aspect words in the vocabulary, where aspects words are filtered through an capsule network with dynamic routing\footnote{This is a key difference from ABAE \cite{He2018ABAE} , in which the mechanism of attention is used to filtering words to aspects.}.
+Each input sample to CBAE is a list of indexes for words in a review sentence.
+First, the model filter away non-aspects words by down-weighting them using an capsule network and construct a sentence embedding $z_s$ from weighted word embeddings.
+Then, the model try to reconstruct the sentence embedding as a linear combination of aspect embedding from $T$.
+This process of dimension reduction and reconstruction, where CBAE aims to transform sentence embeddings of the filtered sentences ($z_s$) into their reconstruction ($r_s$) with the least possible amount of distortion, preserves most of the information of the aspect words in the K embedded aspects.
+This process is described in detail in \cite{He2018ABAE}.
 
-The other possible contents of this section are formulae. They could be on a new line:
-$$S=\pi r^2,$$
-or they could be inline, e.g. if you want to describe the used variables, like $S$ is an area of a circle, while $r$ is its radius.
+\subsection{Sentence Embedding and Capsule Network with dynamic routing}
+
+Capsule network, depicted in Fig.~\ref{fig:capsule} get sentence embedding vector to input.
+It consists of four layers: n-gram convolutional layer, primary capsule layer, secondary capsule layer and fully connected capsule layer.
 
@@
     \centering
-    \includegraphics[width=0.3\linewidth]{circle.png}
-    \caption{A sample circle.}
-    \label{fig:circle}
+    \includegraphics[width=1\linewidth]{rect10315.png}
+    \caption{The Architecture of capsule network for aspect extraction (CBAE encoder part)}
+    \label{fig:capsule}
 \end{figure}
 
+N-gram convolutional layer is a standard convolutional layer which extracts n-gram features at different positions of a sentence through various convolutional filters\cite{Zhao2018} and activated by ELU function.
+Primary capsule layer is the first capsule layer in which the capsules replace the scalar-output feature detectors of CNNs with vector-output capsules to preserve the instantiated parameters sush as the local order of words and semantic representation of words.
+Capsule network tries to address the representational limitation and exponential inefficiencies of convolutions with transformation matrices \cite{Hinton2017DRBC}.
+It allows the networks to automatically learn child-parent relationships constituting viewpoint invariant knowledge that automatically generalizes to novel viewpoints.
+Dynamic routing need to construct a non-linear map in an iterative manner ensuring that the output of each capsule get sent to an appropriate parent in the subsequent layer.
+For each potential parent, the capsule network can increase or decrease the connection strength by dynamic routing, which is more effective than the primitive routing strategies such as max-pooling in CNN that essentially detects whether a feature is present in any position of the text, but loses spatial information about the feature.
+Secondary capsule layer multiply transformation matrices to learn child-parent relationships followed by routing agreement to produce parent capsules in the above.
+Then the capsules from secondary capsule layer flattened into fully connected final capsule then activate by tanh function and normalize by softmax.
+
 \section{Dataset}
-In this section, you need to describe the dataset(s) you are working with. 
-An example dataset we will use is WikiText-2.
-Please mention a paper where it was presented, e.g.
-WikiText-2 was presented in \cite{merity2017pointer}.
-Please provide guidance on how to obtain the dataset\footnote{The one way to do it is to include a link to the website, where it could be downloaded from.
-Like \href{https://blog.einstein.ai/the-wikitext-long-term-dependency-language-modeling-dataset/}{this}.}.
-It is important to mention that the dataset you use must be available for the research purposes.
-So please make sure about that.
+The model have been evaluated on \textbf{Citysearch corpus}.
+This is restaurant review corpus widely used by previous works \cite{Ganu2009BeyondTheStars} \cite{Brody2010UAS} \cite{Zhao2010JMA}, which contains over 50,000 restaurant reviews from Citysearch New York.
+\cite{Ganu2009BeyondTheStars} provided a subset of 3,400 sentences from the corpus with manually labeled aspects.
+These annotated sentences are used for evaluation of aspect identification.
+There are six manually defined aspect labels: \textit{food}, \textit{staff}, \textit{ambience}, \textit{price}, \textit{anecdotes} and \textit{miscellaneous}.
+Corpus prerocessing and word2vect model described in \cite{He2018ABAE}.
 
-Your description will likely be including a table.
-On the Tab.~\ref{tab:statistics} you can see the statistics for the mentioned dataset.
-It is important to notice that there is a split of the dataset and this split is covered by the description.
+\section{Experiments}
+
+\subsection{Metrics}
+The model was evaluated by precision, recall and F1 scores. Сlasses of aspects were put down manually.
+
+\subsection{Experiment Setup}
+For the CBAE and ABAE implementation i repeat parametrs from \cite{He2018ABAE}.
+Initialize the word embedding matrix E with word vectors trained by word2vec with negative sampling on each dataset, setting the embedding size to 200, windows size to 10 and negative sample size to 5.
+The aspect embedding matrix initialized with the centroids of clusters results resulting from running $k$-means on word embeddings.
+Other parameters are initialized randomly.
+During the training process word embedding matrix $E$ was fixed, other parameters optimized using Adam with learning rate 1e-3 for 10 epoch and batch size of 50.
+The number of negative samples was set to 20.
+Following \cite{Brody2010UAS}, \cite{Zhao2010JMA}, \cite{He2018ABAE} the number of aspect for the corpus was set to 14.
+In CBAE like an ABAE, representative  words of an aspect can be found by looking at its nearest words in the embedding space using cosine as the similarity metric.
+
+\subsection{Baselines}
+To validate the performance of CBAE, the model compare with next baselines:
+
+1) \textbf{LocLDA} \cite{Brody2010UAS}: This method uses a standard implementation of LDA.
+
+2) \textbf{$k$-means} \cite{He2018ABAE}: Aspect matrix T with k-means centroids of the word embeddings.
+
+3) \textbf{SAS} \cite{Mukherjee2012}: Hybrid topic model that jointly discovers both aspects and aspect-specific opinions.
+
+4) \textbf{BTM} \cite{Yan2013}: Bitermic topic model that is specially designed for short texts such as texts from social media and review sites.
+The major advantage of BTM over conventional LDA models is that it alleviates the problem of data sparsity in short documents by directly modeling the generation of unordered word-pair co-occurrences (biterms) over the corpus.
+
+5) \textbf{ABAE} \cite{He2018ABAE}: Attention based aspect extraction scores from original papper.
+
+6) \textbf{ABAEr}: ABAE replication on pytorch without ortho regularization.
+
+\section{Results}
+Tab.~\ref{tab:aspects} presents all 14 aspects inferred by CBAE. The inferrent aspects are more finegrained then standard labels.
 
@@
 \begin{center}
-\begin{tabular}[t]{|l|ccc|}
+\begin{tabular}[t]{l|l|l}
 \hline
-%\cline{2-4}
- & Train & Valid & Test \\
+ Inferred Aspects & Representative Words & Gold Aspects \\
 \hline
-Articles & 600 & 60 & 60  \\
-Tokens& 2,088,628 & 217,646 & 245,569 \\
-Vocabulary size & \multicolumn{3}{c|}{33,278} \\
-Out of Vocab rate &  \multicolumn{3}{c|}{2.6\%}  \\
+todo & todo & todo  \\
 \hline
 \end{tabular}
-\caption{Statistics of the WikiText-2.
-The out of vocabulary (OoV) rate notes what percentage of tokens have been replaced by an $\langle unk \rangle$ token.
-The token count includes newlines which add to the structure of the dataset.}
-\label{tab:statistics}
+\caption{List of inferred aspects for restaurant reviews (left), with top representative words for each inferred aspect (middle), and the corresponding gold-standard aspect labels (right).
+Inferred aspect labels (left) were assigned manually.}
+\label{tab:aspects}
 \end{center}
@@
 
-If you were collecting the dataset on your own please describe the collection procedure, like criteria were used to filter the documents, the pre-processing steps, etc.
-It is nice if you release your dataset for the public.
-So please make sure that you have legal rights to collect and distribute the data you were working with.
-We recommend you to look at C4Corpus and how it is licensed to make your corpora.
-C4Corpus is described in \cite{habernal2016c4corpus}.
+Evaluation criterion of sentence-level-aspects identification is to judge how well the predictions match the true labels, measured by precision, recall and $F_1$ scores.
+The results are shown in Tab .~\ref{tab:eval}
 
-\section{Experiments}
-This section should include several subsections.
-\subsection{Metrics}
-First of all, you should describe the metric(s) you were using to evaluate your approach. Most likely a metric description will include a formula.
-
-\subsection{Experiment Setup}
-Secondly, you need to describe the design of your experiment, e.g.
-how many runs there were, how the data split was done.
-The important details of your model, like hyper-parameters used in the experiments, and so on.
-
-\subsection{Baselines}
-Another important feature is that you could provide here the description of some simple approaches for your problem, like logistic regression over TF-IDF embedding for text classification.
-The baselines are needed is there is no previous art on the problem you are presenting.
-
-\section{Results}
-In this section, you need to list and describe the achieved results.
-It is crucial to have the results of the experiments for the other approaches.
-This is needed to be able to compare your results with some competitors.
-Most preferably, you should provide some references with results on the same problem.
-
-Almost inevitably the results are presented as a table, but it is also possible to have a graph, i.e. a figure.
-
-You need also to provide an interpretation of the presented results, to describe some features. E.g. your approach shows higher results on the short texts or by one metric instead of another.
-
-Also in this section, you could provide some results for your model inference. The samples could be found in Tab.~\ref{tab:output}.
-
-\begin{table}[!tbh]
-    \centering
-    \begin{tabular}{|c|}
+\begin{table}[tbh!]
+\begin{center}
+\begin{tabular}[t]{l|l|l|l|l}
 \hline
-Это пример вывода вашей модели на русском.\\
-This is a sample output of your model in English.
-\\
+ Aspect & Method & Precision & Recall & $F_1$ \\
+\hline
+todo & todo & todo & todo & todo  \\
 \hline
 \end{tabular}
-    \caption{Output samples.}
-    \label{tab:output}
+\caption{Aspect identification results on the restaurant domain.
+The results of LocLDA and MELDA are taken from \cite{Zhao2010JMA}; the results of SAS and SERBM are taken from \cite{Wang2015}; the results of k-means and ABAE are taken from \cite{He2018ABAE}}.
+\label{tab:eval}
+\end{center}
 \end{table}
@@
 \section{Conclusion}
-In this section, you need to describe all the work in short: what you have done and what has been achieved.
-E.g.
-you have collected a dataset, made a markup for it and developed a model showing the best results compared to other models.
+TODO
 

### 2020-05-30 paper/main.tex
updated paper

@@
 They also extracted opinion terms by finding the synonyms and antonyms of opinion seed words through WordNet.
-Following this, a number of methods have been proposed based on freequent item mining and dependency information to extract product aspects \cite{Zhuang2006} \cite{Somasundarn2009} \cite{Qiu2011}.
+Following this, a number of methods have been proposed based on freequent item mining and dependency information to extract product aspects \cite{Zhuang2006}
+\cite{Somasundarn2009} \cite{Qiu2011}.
 These models heavily depend on predefined rules which work well only when the aspect terms are restricted to a small group of nouns.
@@
 Aspects are naturally obtained without separately performing extraction and categorization.
-Most existing works \cite{Brody2010UAS} \cite{Zhao2010JMA} \cite{Mukherjee2012} \cite{Chen2014} are based on variants and extensions of LDA \cite{Blei2003}.
+Most existing works \cite{Brody2010UAS} \cite{Zhao2010JMA} \cite{Mukherjee2012} \cite{Chen2014} are based on variants and extensions of LDA
+\cite{Blei2003}.
 Recently, \cite{Wang2015} relies on a substantial amount of prior knowledge such as part-of-speech(POS) tagging and sentiment lexicons.
@@
 \begin{center}
-\begin{tabular}[t]{l|l|l}
+\begin{tabular}[t]{l|l}
 \hline
- Inferred Aspects & Representative Words & Gold Aspects \\
+Representative Words & Aspects \\
 \hline
-todo & todo & todo  \\
+chicken potato onion tomato sauce & food  \\
+highly grilled seared roasted shrimp & food  \\
+pay money leave didn order & price  \\
+minute asked manager seated waiter & staff  \\
+wall room space ceiling lit & ambience  \\
+dish menu entree course flavor & food  \\
+birthday saturday reservation friend friday & anecdotes  \\
+year ny experience life nyc & miscellaneous  \\
+service staff waitstaff attentive friendly & staff  \\
+month time minute week hour & miscellaneous  \\
+drink wine sangria nice perfect & food  \\
+gras crust rib pork foie & food  \\
+chocolate butter fruit sauce sweet & food  \\
+chinese japanese american mexican indian & food  \\
 \hline
 \end{tabular}
-\caption{List of inferred aspects for restaurant reviews (left), with top representative words for each inferred aspect (middle), and the corresponding gold-standard aspect labels (right).
-Inferred aspect labels (left) were assigned manually.}
+\caption{List of top representative words for each aspect (left), and aspect labels (right). Aspect labels (right) were assigned manually.}
 \label{tab:aspects}

### 2020-05-30 paper/main.tex
added final paper

@@
 \usepackage{hyperref}
+\usepackage{breakcites}
 
@@
 Getting labeled datasets is a very expensive and lengthy process.
-In this regard, in the problems of thematic modeling, aspect extraction models from unplaced text is gaining popularity.
-These models allow, with minimal effort to annotate aspects, to structure the text into a set of topics or intentions.
-In this paper, a comparison is made of a SotA model based on attention and a custom model in which the attention mechanism is replaced by a capsule network with dynamic routings.
+In this regard, in the problems of topic modeling, aspect extraction models from unstructured text are gaining popularity.
+These models allow, with minimal effort to annotate aspects to structure the text into a set of topics or intentions.
+In this paper, a comparison is made of a SotA model based on attention and the model in which the attention mechanism is replaced by a capsule network with dynamic routing.
     Codes for paper: \url{https://github.com/KirillKrasikov/TopicModelingWithCapsNet}.
@@
 For example, in the sentence "The beef was tender and melted in my mouth", the aspect term is "beef".
-Two sub-tasks are performed in aspects extraction: (1) extracting all aspects terms(e.g., "beef") from a review corpus, (2) clustering aspect terms with similar meaning into categories where each category represents a single aspect(e.g., cluster "beef", "pork", "pasta", and "tomato" into one aspect food) \cite{He2018ABAE}.
-in 2017 year, Unsupervised Aspect Extraction \cite{He2018ABAE} have become the dominant unsupervised approach for aspect extraction.
-In that work neural word embeddings map words with the same context to nearby points in the embedding space \cite{Mikolov2013W2V}.
-Then attention mechanism \cite{Bahdanau2015NMT} filter the word embeddings within a sentence and filtered words use to construct aspect embeddings.
-The training process for aspect embeddings is analogous to autoencoders, where dimension reduction use to extract the common factors among embedded sentences and reconstruct each sentence through a linear combination of aspect embeddings.
+Two sub-tasks are performed in aspects extraction: (1) extracting all aspects terms(e.g., "beef") from a review corpus, (2) clustering aspect terms with similar meaning into categories where each category represents a single aspect(e.g., cluster "beef", "pork", "pasta", and "tomato" into one aspect \textit{food}) \cite{He2018ABAE}.
+In 2017 year, Unsupervised Aspect Extraction \cite{He2018ABAE} became the dominant unsupervised approach for aspect extraction.
+In that work word embeddings map words with the same context to nearby points in the embedding space \cite{Mikolov2013W2V}.
+Then attention mechanism \cite{Bahdanau2015NMT} filter the word embeddings within a sentence and filtered words are used to construct aspect embeddings.
+The training process for aspect embeddings is analogous with autoencoders, where dimension reduction is used to extract the common factors among embedded sentences and reconstruct each sentence through a linear combination of aspect embeddings.
 The attention mechanism deemphasizes words that are not part of any aspects, allowing the model to focus on aspect words.
-That model call \textit{Attention-based Aspect Extraction} (ABAE).
+That model is called \textit{Attention-based Aspect Extraction} (ABAE).
 In the same year "Google brain" suggested approach called \textit{Dynamic Routing Between Capsules} \cite{Hinton2017DRBC}.
 A capsule is a group of neurons whose activity vector represents the instantiation parameters of a specific type of entity such as an object or an object part.
-The length of the activity vector use to represent the probability that the entity exists and its orientation use to represent the instantiation parameters.
-Active capsules at one level make predictions, via transformation matrices, for the instantiation parameters of higher-level capsules.
-When multiple predictions agree, a higher level capsule becomes active.
-To best performance use iterative routing-by-agreement mechanism: A lower-level capsule prefers to send its output to higher level capsules whose activity vectors have a big scalar product with the prediction coming from the lower-level capsule \cite{Hinton2017DRBC}.
-In this work i implement ABAE model using pytorch, then change attention mechanism to capsule network and evaluate this models on Citysearch corpus used by previous works \cite{Ganu2009BeyondTheStars} \cite{Brody2010UAS} \cite{Zhao2010JMA} \cite{He2018ABAE}.
+The length of the activity vector is used to represent the probability that the entity exists and its orientation is used to represent the instantiation parameters.
+Active capsules at one level make predictions, via transformation n-dimension arrays, for the instantiation parameters of higher-level capsules.
+When multiple predictions mutually adjusted, a higher level capsule becomes active.
+To best performance, iterative routing-by-agreement mechanism is used.
+A lower-level capsule prefers to send its output to higher level capsules whose activity vectors have a big scalar product with the prediction coming from the lower-level capsule \cite{Hinton2017DRBC}.
+In this work an ABAE model is implemented using pytorch, then attention mechanism is changed to capsule network and this model was evaluated on Citysearch corpus used by previous works \cite{Ganu2009BeyondTheStars, Brody2010UAS, Zhao2010JMA, He2018ABAE}.
 
@@
 \label{sec:related}
-The problem of aspect extraction has been well studied in the past decade.
+The problem of aspect extraction was well studied in the past decade.
 Initially, methods were mainly based on manually defined rules.
@@
 They also extracted opinion terms by finding the synonyms and antonyms of opinion seed words through WordNet.
-Following this, a number of methods have been proposed based on freequent item mining and dependency information to extract product aspects \cite{Zhuang2006}
-\cite{Somasundarn2009} \cite{Qiu2011}.
+Following this, a number of methods have been proposed based on frequent item mining and dependency information to extract product aspects \cite{Zhuang2006, Somasundarn2009, Qiu2011}.
 These models heavily depend on predefined rules which work well only when the aspect terms are restricted to a small group of nouns.
 Supervised learning approaches generally model aspect extraction as a standard sequence labeling problem.
-\cite{Jin2009} \cite{Li2010} proposed to use hidden Markov models(HMM) and conditional random fields(CRF) respectively with a set of manually-extracted features.
-More recently, different neural models \cite{Yin2016} \cite{Wang2016} were proposed to automatically learn features for CRF-based aspect extraction.
+\cite{Jin2009, Li2010} proposed to use hidden Markov models(HMM) and conditional random fields(CRF) respectively with a set of manually-extracted features.
+More recently, different neural models \cite{Yin2016, Wang2016} were proposed to automatically learn features for CRF-based aspect extraction.
 Rule-based models are usually not refined enough to categorize the extracted aspect terms.
@@
 Generally, the outputs of those models are word distributions or rankings for each aspect.
-Aspects are naturally obtained without separately performing extraction and categorization.
-Most existing works \cite{Brody2010UAS} \cite{Zhao2010JMA} \cite{Mukherjee2012} \cite{Chen2014} are based on variants and extensions of LDA
-\cite{Blei2003}.
+Aspects are naturally obtained without separately performed extraction and categorization.
+Most existing works \cite{Brody2010UAS, Zhao2010JMA, Mukherjee2012, Chen2014} are based on variants and extensions of LDA \cite{Blei2003}.
 Recently, \cite{Wang2015} relies on a substantial amount of prior knowledge such as part-of-speech(POS) tagging and sentiment lexicons.
-A biterm topic models (BTM) that generates co-occurring word pairs was proposed in \cite{Yan2013}.
+Biterm topic models (BTM) that generate co-occurring word pairs was proposed in \cite{Yan2013}.
 
 Attention models \cite{Mnih2014} have recently gained popularity in training neural networks and have been applied to various natural language processing tasks, including machine translation \cite{Bahdanau2015NMT}, sentence summarization \cite{Rush2015}, sentiment classification \cite{Chen2016} and question answering \cite{Herman2015}.
-Rather than using all available inforamtion, attention mechanism aims to focus on the most pertinent information for a task.
-\cite{He2018ABAE} apply attention to an unsupervised neural model and demonstrate its effectiveness for aspect extraction.
+Rather than using all available information, attention mechanism aims to focus on the most pertinent information for a task.
+\cite{He2018ABAE} applies attention to an unsupervised neural model and demonstrate its effectiveness for aspect extraction.
 
 \cite{Zhao2018} explore capsule networks with dynamic routing process \cite{Hinton2017DRBC} for supervised text classification.
-In this work i apply capsule network with dynamic routing to unsupervised neural model and evaluate experimental results with ABAE and others aspect extraction models.
+In this work capsule network with dynamic routing applied to unsupervised neural model and results are compared with others aspect extraction models.
 
 \section{Model Description}
-
 The ultimate goal of Capsule Based Aspect Extraction (CBAE) is to learn a set of aspect embeddings, where each aspect can be interpreted by looking at the nearest words (representative words) in the embedding space.
 Each word $w$ in vocabulary with a feature vector $e_w \in \R^d$ \cite{He2018ABAE}.
-Word embeddings use to map words that often co-occur in a context to points that are close by in the embedding space \cite{Mikolov2013W2V}.
-The feature vectors associated with the words correspond to the rows of a word embedding matrix $E \in R^{Vd}$, where $V$ is the vocabulary size.
-Model try to learn embeddings of aspects, where aspects share the same embedding space with words.
-This requires an aspect embedding matrix $T \in R^{Vd}$, where $K$ - the number of aspects ($K$ much smaller than $V$).
-The aspect embeddings are use to approximate the aspect words in the vocabulary, where aspects words are filtered through an capsule network with dynamic routing\footnote{This is a key difference from ABAE \cite{He2018ABAE} , in which the mechanism of attention is used to filtering words to aspects.}.
+Word embeddings are used to map words that often co-occur in a context to points that are close by in the embedding space \cite{Mikolov2013W2V}.
+The feature vectors associated with the words correspond to the rows of a word embedding matrix $E \in R^{V \times d}$, where $V$ is the vocabulary size.
+Model tries to learn embeddings of aspects, where aspects share the same embedding space with words.
+This requires an aspect embedding matrix $T \in R^{K \times d}$, where $K$ - the number of aspects ($K$ is much smaller than $V$).
+The aspect embeddings are used to approximate the aspect words in the vocabulary, where aspect words are filtered through the capsule network with dynamic routing\footnote{This is the key difference from ABAE \cite{He2018ABAE} , in which the mechanism of attention is used for filtering words.}.
 Each input sample to CBAE is a list of indexes for words in a review sentence.
-First, the model filter away non-aspects words by down-weighting them using an capsule network and construct a sentence embedding $z_s$ from weighted word embeddings.
-Then, the model try to reconstruct the sentence embedding as a linear combination of aspect embedding from $T$.
-This process of dimension reduction and reconstruction, where CBAE aims to transform sentence embeddings of the filtered sentences ($z_s$) into their reconstruction ($r_s$) with the least possible amount of distortion, preserves most of the information of the aspect words in the K embedded aspects.
+First, the model filter away non-aspect words by down-weighting them using a capsule network and then constructs a sentence embedding $z_s$ from weighted word embeddings.
+Then, the model tries to reconstruct the sentence embedding as a linear combination of aspect embedding from $T$.
+This process of dimension reduction and reconstruction, where CBAE aims to transform sentence embeddings of the filtered sentences ($z_s$) into their reconstruction ($r_s$) with the least possible amount of distortion, preserves most of the information of the aspect words in the $K$ embedded aspects.
 This process is described in detail in \cite{He2018ABAE}.
@@
 \subsection{Sentence Embedding and Capsule Network with dynamic routing}
-
 Capsule network, depicted in Fig.~\ref{fig:capsule} get sentence embedding vector to input.
@@
 N-gram convolutional layer is a standard convolutional layer which extracts n-gram features at different positions of a sentence through various convolutional filters\cite{Zhao2018} and activated by ELU function.
-Primary capsule layer is the first capsule layer in which the capsules replace the scalar-output feature detectors of CNNs with vector-output capsules to preserve the instantiated parameters sush as the local order of words and semantic representation of words.
+Primary capsule layer is the first capsule layer in which the capsules replace the scalar-output feature detectors of CNNs with vector-output capsules to preserve the instantiated parameters such as the local order of words and semantic representation of words.
 Capsule network tries to address the representational limitation and exponential inefficiencies of convolutions with transformation matrices \cite{Hinton2017DRBC}.
 It allows the networks to automatically learn child-parent relationships constituting viewpoint invariant knowledge that automatically generalizes to novel viewpoints.
-Dynamic routing need to construct a non-linear map in an iterative manner ensuring that the output of each capsule get sent to an appropriate parent in the subsequent layer.
+Dynamic routing is needed to construct a non-linear map in an iterative manner ensuring that the output of each capsule gets sent to an appropriate parent in the subsequent layer.
 For each potential parent, the capsule network can increase or decrease the connection strength by dynamic routing, which is more effective than the primitive routing strategies such as max-pooling in CNN that essentially detects whether a feature is present in any position of the text, but loses spatial information about the feature.
-Secondary capsule layer multiply transformation matrices to learn child-parent relationships followed by routing agreement to produce parent capsules in the above.
-Then the capsules from secondary capsule layer flattened into fully connected final capsule then activate by tanh function and normalize by softmax.
+Secondary capsule layer multiplies transformation matrices to learn child-parent relationships followed by routing agreement to produce parent capsules in the above.
+Then the capsules from secondary capsule layer gets flattened into fully connected final capsule, which is then activated by \textit{tanh} function and normalized by \textit{softmax}.
 
@@
 The model have been evaluated on \textbf{Citysearch corpus}.
-This is restaurant review corpus widely used by previous works \cite{Ganu2009BeyondTheStars} \cite{Brody2010UAS} \cite{Zhao2010JMA}, which contains over 50,000 restaurant reviews from Citysearch New York.
+This is restaurant review corpus widely used by previous works \cite{Ganu2009BeyondTheStars, Brody2010UAS, Zhao2010JMA}, which contains over 50,000 restaurant reviews from Citysearch New York.
 \cite{Ganu2009BeyondTheStars} provided a subset of 3,400 sentences from the corpus with manually labeled aspects.
@@
 There are six manually defined aspect labels: \textit{food}, \textit{staff}, \textit{ambience}, \textit{price}, \textit{anecdotes} and \textit{miscellaneous}.
-Corpus prerocessing and word2vect model described in \cite{He2018ABAE}.
+Corpus preprocessing is described in \cite{He2018ABAE}.
 
@@
 \subsection{Metrics}
-The model was evaluated by precision, recall and F1 scores. Сlasses of aspects were put down manually.
+The model was evaluated by precision, recall and F1 scores. Сlasses of aspects were tagged manually.
 
 \subsection{Experiment Setup}
-For the CBAE and ABAE implementation i repeat parametrs from \cite{He2018ABAE}.
-Initialize the word embedding matrix E with word vectors trained by word2vec with negative sampling on each dataset, setting the embedding size to 200, windows size to 10 and negative sample size to 5.
+For the CBAE implementation word embedding matrix E with word vectors trained by word2vec with negative sampling on each dataset.
+Settings of the word2vec parameters: embedding size = 200, window size = 10 and negative sample size = 5.
 The aspect embedding matrix initialized with the centroids of clusters results resulting from running $k$-means on word embeddings.
 Other parameters are initialized randomly.
-During the training process word embedding matrix $E$ was fixed, other parameters optimized using Adam with learning rate 1e-3 for 10 epoch and batch size of 50.
+During the training process word embedding matrix $E$ was fixed, other parameters were optimized using \textit{Adam} with learning rate 1e-3 for 10 epochs and batch size of 50.
 The number of negative samples was set to 20.
-Following \cite{Brody2010UAS}, \cite{Zhao2010JMA}, \cite{He2018ABAE} the number of aspect for the corpus was set to 14.
-In CBAE like an ABAE, representative  words of an aspect can be found by looking at its nearest words in the embedding space using cosine as the similarity metric.
+Following \cite{Brody2010UAS, Zhao2010JMA, He2018ABAE} the number of aspects for the corpus was set to 14.
+In CBAE like in ABAE, representative  words of an aspect can be found by looking at its nearest words in the embedding space using cosine as the similarity metric.
+N-gram convolutional layer setting the kernel size to 3, stride to 1 and channels to 200.
+Primary caps layer has 7 capsules with kernel size = 3, stride = 1 and out channels = 32, Secondary capsule layer has 7 capsules with 32 channels.
+Dynamic routing performs 3 iterations.
 
 \subsection{Baselines}
-To validate the performance of CBAE, the model compare with next baselines:
+To validate the performance of CBAE, the model was compared with next baselines:
 
@@
 
-5) \textbf{ABAE} \cite{He2018ABAE}: Attention based aspect extraction scores from original papper.
-
-6) \textbf{ABAEr}: ABAE replication on pytorch without ortho regularization.
+5) \textbf{ABAE} \cite{He2018ABAE}: Attention based aspect extraction.
 
 \section{Results}
-Tab.~\ref{tab:aspects} presents all 14 aspects inferred by CBAE. The inferrent aspects are more finegrained then standard labels.
+Tab.~\ref{tab:aspects} presents all 14 aspects inferred by CBAE.
 
@@
 
-Evaluation criterion of sentence-level-aspects identification is to judge how well the predictions match the true labels, measured by precision, recall and $F_1$ scores.
-The results are shown in Tab .~\ref{tab:eval}
-
 \begin{table}[tbh!]
@@
 \hline
-todo & todo & todo & todo & todo  \\
+          & LocLDA      & 0.90          & 0.65          & 0.75           \\
+          & SAS         & 0.88          & 0.77          & 0.82           \\
+          & BTM         & 0.93          & 0.75          & 0.82           \\
+food      & k-means     & 0.93          & 0.65          & 0.76           \\
+          & ABAE        & \textbf{0.95} & 0.74          & 0.83           \\
+          & CBAE        & 0.89          & \textbf{0.85} & \textbf{0.87}  \\
+\hline
+          & LocLDA      & 0.80          & 0.59          & 0.68           \\
+          & SAS         & 0.77          & 0.56          & 0.65           \\
+          & BTM         & \textbf{0.83} & 0.58          & 0.68           \\
+staff     & k-means     & 0.79          & 0.69          & 0.66           \\
+          & ABAE        & 0.80          & 0.73          & \textbf{0.77}  \\
+          & CBAE        & 0.68          & \textbf{0.75} & 0.71           \\
+\hline
+          & LocLDA      & 0.60          & 0.68          & 0.64           \\
+          & SAS         & 0.78          & 0.54          & 0.65           \\
+          & BTM         & 0.81          & 0.6           & 0.69           \\
+ambience  & k-means     & 0.73          & 0.64          & 0.68           \\
+          & ABAE        & 0.82          & \textbf{0.70} & \textbf{0.74}  \\
+          & CBAE        & \textbf{0.83} & 0.62          & 0.71           \\
 \hline
 \end{tabular}
-\caption{Aspect identification results on the restaurant domain.
-The results of LocLDA and MELDA are taken from \cite{Zhao2010JMA}; the results of SAS and SERBM are taken from \cite{Wang2015}; the results of k-means and ABAE are taken from \cite{He2018ABAE}}.
+\caption{Aspect identification results.
+The result of LocLDA is taken from \cite{Zhao2010JMA}; the result of SAS is taken from \cite{Wang2015}; the results of BTM, k-means and ABAE are taken from \cite{He2018ABAE}}.
 \label{tab:eval}
@@
 
+Evaluation criterion of sentence-level-aspects identification is to judge how well the predictions match the true labels.
+It is measured by precision, recall and $F_1$ scores.
+The results are shown in Tab .~\ref{tab:eval}
+
 \section{Conclusion}
-TODO
+The analysis of the results shows that the attention-based model in general has more scores.
+Greater recall of capsule-based model is determined by the lower severity of aspects relative to the attention-based model (for example \textit{nice} and \textit{perfect} with \textit{drink} and \textit{wine} or \textit{leave} with \textit{pay} and \textit{money}).
+Perhaps the orchestration of these models will make it possible to obtain higher marks in the problem of aspect extraction.
+\\ \\ \\ \\ \\ \\
 

### 2020-05-30 desc/main.tex
Models and description (#1)
* added ABAE pipe

* added CBAE model

* updated CBAE

* refactored CBAE pipeline

* updated CBAE

* added CBAE validate pipeline

* added dataset, dataset loader

* updated train pipeline

* added CBAE baseline

* 23/65/27

* added tex

* updated paper

* 11/65/53

* added worked abae

* 73/86/69

* 78/88/73

* added ABAE baseline

* CBAE 61/83/69

* CBAE 64/84/69

* updated paper

* added paper introduction

* added related work

* added model description

* added experiment template

* added CBAE results

* updated paper

* added final paper

* updated models

*

--- 2020-05-30 paper/main.tex
@@
 These models allow, with minimal effort to annotate aspects to structure the text into a set of topics or intentions.
-In this paper, a comparison is made of a SotA model based on attention and the model in which the attention mechanism is replaced by a capsule network with dynamic routing.
-    Codes for paper: \url{https://github.com/KirillKrasikov/TopicModelingWithCapsNet}.
+In this desc, a comparison is made of a SotA model based on attention and the model in which the attention mechanism is replaced by a capsule network with dynamic routing.
+    Codes for desc: \url{https://github.com/KirillKrasikov/TopicModelingWithCapsNet}.
 \end{abstract}
